Rising from the Ashes: How the Milky Way Got Its Scars

### 2024-04-29 paper/ms.tex
Paper updates
Rename sec to src
Move and update abstract

\begin{abstract}
  The nuclear abundance distribution of stars encodes the history of the gas-phase abundance in the Milky Way. Without a large, unbiased sample of stellar ages, the exact timing and nature of this history must be \textit{inferred} from the abundances. In the two-dimensional plane of \alphaFe-\FeH, it is now clear that two separate populations exist - the low-$\alpha$ and high-$\alpha$ sequences. A restatement of this fact is that the distribution of \alphaFe{} is bimodal at a fixed Fe. Structure in the nuclear abundance distribution can arise from many processes - proposals include radial migration, high-redshift clump formation, and various effects associated with galaxy mergers, among others. In this work, we demonstrate another possible avenue for structure formation with clear observational predictions. We propose that the Galaxy underwent a starburst followed by a brief (hundreds of Myr) quiescent phase. A natural consequence of this quiescent phase is that stars in the valley of the bimodality do not form because: (1) the absence of enrichment from high-mass stars leads to a rapid reduction in \alphaFe{}, and (2) any time the gas spends in the abundance valley is deemphasized in the present day distribution because the star formation rate is lower. With a set of idealized merger simulations, we demonstrate the feasibility of this proposal. The starburst and quiescent phase can result from a merger, but it is not a necessary component of the theory. This ``phoenix hypothesis'' predicts a gap in stellar ages at a fixed \FeH{} and that stars which form directly after this gap would have lower \alphaFe{} than stars which form slightly later.
\end{abstract}

\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of 
astronomy(1868) --- Interdisciplinary astronomy(804)}

\input{sec/int.tex}

\input{sec/met.tex}

\input{sec/res.tex}

\input{sec/dis.tex}

\input{sec/con.tex}

@@

\bibliography{ref}{}
\bibliographystyle{aasjournal}

% \input{app.tex}

>>>>

\input{src/abs.tex}

\input{src/int.tex}

\input{src/met.tex}

\input{src/res.tex}

\input{src/dis.tex}

\input{src/con.tex}

@@

\bibliography{src/ref}{}
\bibliographystyle{aasjournal}

\input{src/app.tex}
